# IRIS data Clustering
## Grip Internship

Reading the dataset
```{r}
df <- iris
head(df)
```
creating a dataframe withiut species column
```{r}
df <- df[,1:4]
```
Dimensions and structure of the dataset
```{r}
dim(df)
str(df)
```
Loading the required libraries
```{r}
library(cluster)
library(factoextra)
```
Finding optimum number of cluster using Elbow method
```{r}
fviz_nbclust(df, kmeans, method = 'wss') +
  geom_vline(xintercept = 3, linetype = 5, col = 'orange')
```
#so looking at the elbow curve.. its is wise to use three clusters



K MEANS CLUSTERING
```{r}
set.seed(123)
km.res= kmeans(df, 3, nstart = 40)
```

INFORMATION ABOUT CLUSTERS
```{r}
print(km.res)
```
Visual Representation of Cluster
```{r}
fviz_cluster(km.res, data = df,
             palette = c('#2E9FDF', '#E7B800', '#FC4E07'),
             ellipse = TRUE,
             ellipse.type = "convex",
             show.clust.cent = FALSE,
             ggtheme = theme_classic())
```
PROFILE OF EACH CLISTER
SEE MEANS OF VARIABLES IN ORIGINAL DATA, CLUSTER WISE
```{r}
aggregate(df, by = list(cluster = km.res$cluster), mean)
```
HIERARCHICAL CLUSTERING
```{r}
res.dist = dist(df, method = 'euclidean')
res.hc= hclust(d = res.dist, method = 'ward.D2')
fviz_dend(res.hc, k = 3,
          cex = 0.5,
          k_colors = c('#2E9FDF', '#FC4E07', '#E7B800'),
          color_labels_by_k = TRUE,
          rect = TRUE)
```
